---
title: "Informattion Science3"
subtitle: "Assignment3"
author: "Nobuoka Yuki (1240492)"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
    toc: false
    number_sections: FALSE
  html_document:
    highlight: tango
    theme: united
    toc: true
    smart: false
    css: my-markdown.css
header-includes:
  - \usepackage{indentfirst}
  - \parindent = 1em
  - \usepackage{dcolumn}
  - \newcolumntype{.}{D{.}{.}{-1}}
  - \usepackage{caption}
  - \captionsetup[table]{name=表}
  - \captionsetup[figure]{name=図}
  - \usepackage{hyperref}
documentclass: bxjsarticle
classoption: 11pt,a4paper,lualatex,ja=standard
---

```{r global_option, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,      # Rコード: FALSE で非表示, TRUE で表示
                      warning = FALSE,  # 警告文: FALSE で非表示, TRUE で表示
                      message = FALSE,  # メッセージ: FALSE で非表示, TRUE で表示
                      fig.width = 5,    # 図の幅の既定値
                      fig.height = 3)   # 図の高さの既定値
## PDF に出力する際は cairo を使用する
if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(dev = "cairo_pdf")
}
```


```{r, include=FALSE}
pacman::p_load(tidyverse, 
               fontregisterer)
```


```{r, include=FALSE}
library(fontregisterer)
my_font <- "Yu Gothic"
## ggplot2 用の設定
theme_set(theme_gray(base_size = 9,
                     base_family = my_font))
```


# 1

```{r}
mpg %>% 
  group_by(class) %>% 
  summarise(cty,
            displ,
            .groups = "drop") %>% 
  ggplot() +
  geom_point(aes(x = displ, y = cty, color = class), size = 1) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Engine displacement (litter)", y = "City miles per gallon", color = "Class")
  
```

```{r}
mpg %>% 
  group_by(class) %>% 
  summarise(cty,
            displ,
            .groups = "drop") %>% 
  ggplot() +
  geom_point(aes(x = displ, y = cty, color = class), color = "black",size = 0.5) +
  labs(x = "Engine displacement (litter)", y = "City miles per gallon") +
  facet_wrap(~ class, ncol = 3)
```

# 2

```{r}
ggplot(economics, aes(x = date, y = unemploy)) +
  geom_rect(data = presidential, aes(NULL,NULL,
                                     xmin = start, xmax = end, fill = party),
            ymin = 0, ymax = 16000, alpha = 0.4, alpha = 0.1,colour = "gray") +
  geom_line(size = 0.5) +
  scale_fill_manual(values = c("Democratic" = "#6495ED", 
                               "Republican" = "#F08080")) +
  geom_text(data=presidential,aes(x=start, y=3000,label=name), size=2, hjust = 0) +
  labs(title = "Unemployment in the US", x = "Date", y = "Unemployment",
       fill = "Government")
```


# 3 

```{r}
data <- tibble(
  year = c(1980, 1985, 1990, 2000, 2010, 2015, 2019),
  values = c(24728221, 24717566, 24621173, 24490387, 24461631, 24432757, 24436003)
)
```

```{r}
data %>% 
  ggplot(aes(x = as.factor(year), y = values/10000, group = 1)) +
  geom_line(color = "#7B68EE", size = 1) +
  geom_point(color = "#7B68EE", size = 3) +
  scale_y_continuous(breaks = seq(0, 2500)) +
  ylim(c(0, 2500)) +
  labs(x = "year", y = "are (10000ha)") +
  theme_classic()
                     
```


This graph show forest area in Japan from 1980-2019[(統計Dashboard)](https://dashboard.e-stat.go.jp/graph?screenCode=00640). The best thing about this graph is that it allows interactive manipulation. The viewer can see more detailed values by moving the cursor over the line. However, this graph has some improvements. Sine this graph uses a line graph, it can be inferred that the purpose is to convey changes in forest area over time. In this graph, the y-axis stars at 0, making it difficult to see the degree of change. If the creator of this graph wants to claim that "forest area is declining" they need to adjust the y-axis. In addition, the x-axis also needs to be improved as the period and width of the axis do not match. In the image below, the width of the y-axis has been adjusted, and the width the x-axis corresponds to "year"


```{r}
data %>% 
  ggplot(aes(x = year, y = values/10000, group = 1)) +
  geom_line(colour = "#7B68EE", size = 1) +
  geom_point(size = 3, colour = "#7B68EE", fill = "#7B68EE") +
  labs(x = "Year", y = "ara (10000 ha)") +
  scale_x_continuous(breaks = c(1980, 1985, 1990, 2000, 2010, 2015, 2019),
                     labels = c(1980, 1985, 1990, 2000, 2010, 2015, 2019)) +
  ggtitle("Forest area")
```

















