---
title: |
  | Final Project Presentation
subtitle: "Infomation Science3"
author: "Nobuoka Yuki"
date: "2022年11月28日"
output: 
  beamer_presentation:
    theme: QPE
    highlight: zenburn
    latex_engine: lualatex
    fig_caption: false #プレゼンの図はキャプション不要（スライドタイトルを使う）
header-includes:
  - \institute[矢内研]{計量政治経済研究室}
classoption: unicode
---
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.height = 8, 
                      fig.width = 12,
                      dev = "cairo_pdf")
```

```{r load_packs, include = FALSE, results = 'hide'}
## 利用するパッケージを忘れずに読み込む
pacman::p_load(tidyverse,
               estimatr,
               texreg,
               palmerpenguins)

## ggplot2 で使うフォントの設定：Windows, macOS, Ubuntu に対応
if (Sys.info()["sysname"] == "Windows") { # Windows用
  if (!require(fontregisterer)) {
    pacman::p_load(systemfonts)
    remotes::install_github("Gedevan-Aleksizde/fontregisterer",
                            repos = NULL, type = "source")
  }
  library(fontregisterer)
  my_font <- "IPAexGothic"
} else { # macOS と Ubuntu 用
  my_font <- "IPAexGothic"
  #my_font <- "HiraginoSans-W3" # macOS でヒラギノを使う場合はこれ
}
theme_set(theme_light(base_size = 24,
                         base_family = my_font))

# ggplot2のテーマをスライド用に変更
qpe_theme <- theme(
  plot.background = element_rect(fill = "gray87",
                                 color = NA),
  legend.key = element_rect(fill = "white",
                            color = "white"),
  legend.background = element_rect(fill = "gray87",
                                   color = NA),
  legend.key.size = unit(25, "mm"))
```

```{r, include=FALSE}
 #データの読み込み
data <- read.csv("OLYMPICS_athlete_events.csv")
#1980年以降の大会を抽出
data <- data %>%                           
  filter(Year >= 1980) %>% 
  select(Year,NOC, City, Medal, Sex, Season) %>% 
  arrange(Year)
#開催国と選手の出身国の表記を統一
data <- data %>%    
  mutate(City = str_replace_all(City, pattern = c("Lake Placid" = "USA",
                                                  "Moskva" = "RUS",
                                                  "Sarajevo" = "YUG",
                                                  "Los Angeles" = "USA",
                                                  "Calgary" = "CAN",
                                                  "Seoul" = "KOR",
                                                  "Barcelona" = "ESP",
                                                  "Albertville" = "FRA",
                                                  "Lillehammer" = "NOR",
                                                  "Atlanta" = "USA",
                                                  "Nagano" = "JPN",
                                                  "Sydney" = "AUS",
                                                  "Salt Lake City" = "USA",
                                                  "Athina" = "GRE",
                                                  "Torino" = "ITA",
                                                  "Beijing" = "CHN",
                                                  "Vancouver" = "CAN",
                                                  "London" = "GBR",
                                                  "Sochi" = "RUS",
                                                  "Rio de Janeiro" = "BRA")))

#開催国か否かの変数を追加
data <- data %>%
  mutate(Situation = ifelse(NOC == City, "Host", "Guest"))

#冬と夏を区別（文字列を操作）
data <- data %>%  
# mutate(Year_place = paste(!!!rlang::syms(c("Year", "Season")), sep = "_"))
  mutate(Year_place = str_c(Year, Season, sep = "_"))
```


# Introduction

## Story

\LARGE

- Get more medals at the Olympics held in home country than held in other countries

## Background

\LARGE

- low physical burden of traveling
- experiential knowledge
- sports enhancement strategy by government


# Visualization

## Number of medals by country

```{r, include=FALSE}
Year_Medal_data <- data %>%
  group_by(Year,Year_place, NOC) %>% 
  # 年と国ごとにメダル数をカウント
  summarise(Medal_count = sum(ifelse(is.na(Medal), 0, 1)), #NAがあるときはis.na()
            Situation = Situation[1],  #これの方が分かりやすい
            Sensyu = length(NOC),
            Medal_per = (Medal_count / Sensyu) * 100, #1人当たりのメダル獲得数
            Season = max(Season),
            .groups = "drop")

Year_Medal_data <- Year_Medal_data %>%    #開催したことのある国だけを抽出
  filter(NOC %in% unique(data$City))

fig1 <- Year_Medal_data %>% 
  ggplot() +
  geom_boxplot(aes(x = NOC, y = Medal_count), outlier.shape = NA) +
  geom_point(aes(x = NOC, y = Medal_count, color = Situation),
             alpha = 0.7, size = 2) +
  scale_colour_manual(values = c("gray", "red")) +
  theme(legend.position = "bottom") +
  labs(x = "Country", y = "Number of Medals") +
  theme(axis.text  = element_text(size = rel(0.6)),
        strip.background = element_rect(fill = "gray", color = "black"),
        strip.text = element_text(size = rel(1.2), color = "black"))
```

```{r}
plot(fig1 + qpe_theme)
```

## Average number of medals won per country

```{r, include=FALSE}
Year_Medal_data4 <- tibble(
  Season = rep("Season", 4*length(unique(Year_Medal_data$NOC))),
  NOC = rep("NOC", 4*length(unique(Year_Medal_data$NOC))),
  Situation = rep("Kaisai", 4*length(unique(Year_Medal_data$NOC))),
  Medal_count = rep(0, 4*length(unique(Year_Medal_data$NOC)))
)

n <- 1

for (i in unique(Year_Medal_data$NOC)) {
   df1 <- Year_Medal_data %>% 
    filter(NOC == i)
   
   #夏開催で非開催地
   df2 <- df1 %>% 
     filter(Season == "Summer")
   df3 <- df2 %>% 
     filter(Situation == "Guest")
   S_G_medal <- round(mean(df3$Medal_count), digits = 2)
   Year_Medal_data4[n, 1] <- "Summer"
   Year_Medal_data4[n, 2] <- i
   Year_Medal_data4[n, 3] <- "Guest"
   Year_Medal_data4[n, 4] <- S_G_medal
   
   #夏開催で開催地
   df3 <- df2 %>% 
     filter(Situation == "Host")
   S_H_medal <- round(mean(df3$Medal_count), digits = 2)
   Year_Medal_data4[n + 1, 1] <- "Summer"
   Year_Medal_data4[n + 1, 2] <- i
   Year_Medal_data4[n + 1, 3] <- "Host"
   Year_Medal_data4[n + 1, 4] <- S_H_medal
   
   #冬開催で非開催地
   df2 <- df1 %>% 
     filter(Season == "Winter")
   df3 <- df2 %>% 
     filter(Situation == "Guest")
   W_G_medal <- round(mean(df3$Medal_count), digits = 2)
   Year_Medal_data4[n + 2, 1] <- "Winter"
   Year_Medal_data4[n + 2, 2] <- i
   Year_Medal_data4[n + 2, 3] <- "Guest"
   Year_Medal_data4[n + 2, 4] <- W_G_medal
   
   #冬開催で開催地
   df3 <- df2 %>% 
     filter(Situation == "Host")
   W_H_medal <- round(mean(df3$Medal_count), digits = 2)
   Year_Medal_data4[n + 3, 1] <- "Winter"
   Year_Medal_data4[n + 3, 2] <- i
   Year_Medal_data4[n + 3, 3] <- "Host"
   Year_Medal_data4[n + 3, 4] <- W_H_medal
   
   n <- n + 4
}

fig2 <- Year_Medal_data4 %>% 
  ggplot() +
  geom_bar(aes(x = NOC, y = Medal_count, fill = Situation), 
           stat = "identity", position = "dodge") +
  facet_wrap(~ Season, ncol = 1, scales = "free_y") +
  labs(x = "Country", y = "Average Number of Medals") +
  scale_fill_manual(values = c("gray", "#ff5252")) +
  theme(strip.background = element_rect(fill = "gray", color = "black"),
        strip.text = element_text(size = rel(1.2), color = "black"),
        axis.text  = element_text(size = rel(0.6)))

```

```{r}
plot(fig2 + qpe_theme)
```

## Changes in the number of medals (Summer)

```{r}
fig3 <- Year_Medal_data %>%
  filter(Season == "Summer") %>% 
  ggplot() +
  geom_line(aes(x = Year, y = Medal_count, group = 1), size = 0.8) +
  geom_point(aes(x = Year, y = Medal_count, color = Situation), size = 1.6) +
  scale_colour_manual(values = c("black", "red")) +
  facet_wrap(~ NOC, ncol = 4) +
  labs(x = "Country", y = "Number of Medals") +
  theme(strip.background = element_rect(fill = "gray", color = "black"),
        strip.text = element_text(size = rel(0.5), color = "black"),
        axis.text  = element_text(size = rel(0.5)))
plot(fig3 + qpe_theme)
```

## Changes in the number of medals (Winter)

```{r}
fig4 <- Year_Medal_data %>%
  filter(Season == "Winter") %>% 
  ggplot() +
  geom_line(aes(x = Year, y = Medal_count, group = 1), size = 0.8) +
  geom_point(aes(x = Year, y = Medal_count, color = Situation), size = 1.6) +
  scale_colour_manual(values = c("black", "red")) +
  facet_wrap(~ NOC, ncol = 4) +
  labs(x = "Country", y = "Number of Medals") +
  theme(strip.background = element_rect(fill = "gray", color = "black"),
        strip.text = element_text(size = rel(0.5), color = "black"),
        axis.text  = element_text(size = rel(0.5)))
plot(fig4 + qpe_theme)
```


# Conclusion

## Conclusion

\begin{alertblock}{story}
 Get more medals at the Olympics held in your own country than when they are held in other countries
\end{alertblock}

\begin{block}{Conclusion}
 \begin{itemize}
   \item The figures reflected the story
   \item Also be able to read the background of the story from these figures
 \end{itemize}
\end{block}
